Technique for \earlywarning\ detection of compact binary coalescence and its implications for multi-messenger astronomy

### 2011-06-09 implementation.tex
Converted some software citations to links
git-svn-id: https://svn.ligo.caltech.edu/svn/6th-Floor-Papers/lloid_paper@995 ccdd05d5-56c1-461a-bf98-85f6876523b4

We have implemented a prototype of the low-latency filtering stage using an
open-source signal processing environment called \gstreamer\ \cite{gstreamer}.
\gstreamer\ is a vital component of many Linux systems, providing media
playback, authoring, and streaming on devices from cell phones to desktop
computers to streaming media servers.  Given the similarities of
\GW{} detector data to audio data it is not surprising that
\gstreamer\ is useful for our purpose. \gstreamer\ also provides some useful
stock signal processing elements such as re-samplers and filters.  We have
extended the \gstreamer\ framework by developing a library called
\gstlal{}~\cite{gstlal} that provides elements for \GW{} data
analysis.

>>>>

We have implemented a prototype of the low-latency filtering stage using an
open-source signal processing environment called
\gstreamer\footnote{\url{http://gstreamer.net/}}.
\gstreamer\ is a vital component of many Linux systems, providing media
playback, authoring, and streaming on devices from cell phones to desktop
computers to streaming media servers.  Given the similarities of
\GW{} detector data to audio data it is not surprising that
\gstreamer\ is useful for our purpose. \gstreamer\ also provides some useful
stock signal processing elements such as re-samplers and filters.  We have
extended the \gstreamer\ framework by developing a library called
\gstlal\footnote{\url{https://www.lsc-group.phys.uwm.edu/daswg/projects/gstlal.html}}
that provides elements for \GW{} data analysis.

### 2011-06-09 results.tex
Converted some software citations to links
git-svn-id: https://svn.ligo.caltech.edu/svn/6th-Floor-Papers/lloid_paper@995 ccdd05d5-56c1-461a-bf98-85f6876523b4

We examine the performance of the \lloid\ algorithm on a small region of
compact binary parameter space centered on typical \textsc{ns}--\textsc{ns}
masses.  We begin by constructing a template bank that spans component masses
between 1~and~3~$M_\odot$ using a simulated Advanced \LIGO{} noise
curve~\cite{lal}.  Then we create sub-banks by partitioning the parameter space by
chirp mass.  Figure \ref{fig:tmpltbank} illustrates this procedure.
\begin{figure}[htbp]
	\begin{center}
		\includegraphics{figures/tmpltbank.png}
		\caption{\label{fig:tmpltbank}Placement of template parameters used in this paper.  The template bank consists of 98544 templates with component masses $m_1$, $m_2$, between 1~and~3~$M_\odot$.  We design a filter bank to search for a subset of 657 of these templates with chirp masses $\mathcal M$ between 1.1955~and~1.2045~$M_\odot$.}
	\end{center}
\end{figure}
The result is that we obtain 657 templates with chirp masses between 1.1955~and~1.2045~$M_\odot$.  With this
sub-bank we were able to construct an efficient time-slice decomposition that consisted of 11 time slices
with sample rates between 32 and 4096 Hz shown in table \ref{tab:time_slices}.
\begin{table}
\begin{indented}
\caption{\label{tab:time_slices} Filter design for these 657 templates.  From left to right, this table shows the sample rate, time interval, number of samples, and number of orthogonal templates for each time slice.  We vary \SVD{} tolerance from $\left(1-10^{-1}\right)$ to $\left(1-10^{-6}\right)$.}
\item[]\begin{tabular}{rr@{,\,}lc*{6}{r}}
\br
\multicolumn{4}{c}{} &\centre{6}{$\log_{10}$ (1$-$\SVD{} tolerance)} \\
\ns
\multicolumn{4}{c}{} &\crule{6} \\
$f^s$ (Hz) & $[t^s$&$t^{s+1})$ (s) & $N^s$ & $-1$ & $-2$ & $-3$ & $-4$ & $-5$ & $-6$ \\
\mr
4096 & [0&0.5) & 2048 & 1 & 4 & 6 & 8 & 10 & 14 \\
512 & [0.5&4.5) & 2048 & 2 & 6 & 8 & 10 & 12 & 16 \\
256 & [4.5&12.5) & 2048 & 2 & 6 & 8 & 10 & 12 & 15 \\
128 & [12.5&76.5) & 8192 & 6 & 20 & 25 & 28 & 30 & 32 \\
64 & [76.5&140.5) & 4096 & 1 & 8 & 15 & 18 & 20 & 22 \\
64 & [140.5&268.5) & 8192 & 1 & 7 & 21 & 25 & 28 & 30 \\
64 & [268.5&396.5) & 8192 & 1 & 1 & 15 & 20 & 23 & 25 \\
32 & [396.5&460.5) & 2048 & 1 & 1 & 3 & 9 & 12 & 14 \\
32 & [460.5&588.5) & 4096 & 1 & 1 & 7 & 16 & 18 & 21 \\
32 & [588.5&844.5) & 8192 & 1 & 1 & 8 & 26 & 30 & 33 \\
32 & [844.5&1100.5) & 8192 & 1 & 1 & 1 & 12 & 20 & 23 \\
\br
\end{tabular}
\end{indented}
\end{table}
We use this template bank and decomposition for the remainder of this section.

>>>>

We examine the performance of the \lloid\ algorithm on a small region of
compact binary parameter space centered on typical \textsc{ns}--\textsc{ns}
masses.  We begin by constructing a template bank that spans component masses
between 1~and~3~$M_\odot$ using a simulated Advanced \LIGO{} noise
curve~\cite{ALIGONoise}.  Then we create sub-banks by partitioning the parameter
space by chirp mass.  Figure \ref{fig:tmpltbank} illustrates this procedure.
\begin{figure}[htbp]
	\begin{center}
		\includegraphics{figures/tmpltbank.png}
		\caption{\label{fig:tmpltbank}Placement of template parameters used in this paper.  The template bank consists of 98544 templates with component masses $m_1$, $m_2$, between 1~and~3~$M_\odot$.  We design a filter bank to search for a subset of 657 of these templates with chirp masses $\mathcal M$ between 1.1955~and~1.2045~$M_\odot$.}
	\end{center}
\end{figure}
The result is that we obtain 657 templates with chirp masses between 1.1955~and~1.2045~$M_\odot$.  With this
sub-bank we were able to construct an efficient time-slice decomposition that consisted of 11 time slices
with sample rates between 32 and 4096 Hz shown in table \ref{tab:time_slices}.
\begin{table}
\begin{indented}
\caption{\label{tab:time_slices} Filter design for these 657 templates.  From left to right, this table shows the sample rate, time interval, number of samples, and number of orthogonal templates for each time slice.  We vary \SVD{} tolerance from $\left(1-10^{-1}\right)$ to $\left(1-10^{-6}\right)$.}
\item[]\begin{tabular}{rr@{,\,}lc*{6}{r}}
\br
\multicolumn{4}{c}{} &\centre{6}{$\log_{10}$ (1$-$\SVD{} tolerance)} \\
\ns
\multicolumn{4}{c}{} &\crule{6} \\
$f^s$ (Hz) & $[t^s$&$t^{s+1})$ (s) & $N^s$ & $-1$ & $-2$ & $-3$ & $-4$ & $-5$ & $-6$ \\
\mr
4096 & [0&0.5) & 2048 & 1 & 4 & 6 & 8 & 10 & 14 \\
512 & [0.5&4.5) & 2048 & 2 & 6 & 8 & 10 & 12 & 16 \\
256 & [4.5&12.5) & 2048 & 2 & 6 & 8 & 10 & 12 & 15 \\
128 & [12.5&76.5) & 8192 & 6 & 20 & 25 & 28 & 30 & 32 \\
64 & [76.5&140.5) & 4096 & 1 & 8 & 15 & 18 & 20 & 22 \\
64 & [140.5&268.5) & 8192 & 1 & 7 & 21 & 25 & 28 & 30 \\
64 & [268.5&396.5) & 8192 & 1 & 1 & 15 & 20 & 23 & 25 \\
32 & [396.5&460.5) & 2048 & 1 & 1 & 3 & 9 & 12 & 14 \\
32 & [460.5&588.5) & 4096 & 1 & 1 & 7 & 16 & 18 & 21 \\
32 & [588.5&844.5) & 8192 & 1 & 1 & 8 & 26 & 30 & 33 \\
32 & [844.5&1100.5) & 8192 & 1 & 1 & 1 & 12 & 20 & 23 \\
\br
\end{tabular}
\end{indented}
\end{table}
We use this template bank and decomposition for the remainder of this section.
